Turbo fast no compromise gravitational wave parameter estimation

### 2023-01-08 src/tex/ms.tex
Shrink table size

\section{Result}
\label{sec: Result}

\begin{enumerate}
    \item ppplot
    \item real-event result
\end{enumerate}

\subsection{Injection-recovery test}

@@

\begin{table*}[hbt!]
    \begin{center}
    \begin{tabular}{ l l l }
    \hline
    \hline
    Parameters &  Description & Prior range\\

    $M_c$ & chirp mass & $[10, 50] M_\odot$\\
    $q$ & mass ratio & $[0.5, 1]$\\
    $\chi_1$ & dimensionless spin of the primary mass & $[-0.5, 0.5]$\\
    $\chi_2$ & dimensionless spin of the secondary mass & $[-0.5, 0.5]$\\
    $d_L$ & luminosity distance & $[300, 2000] Mpc$\\
    $t_c$ & coalescence time & $[-0.5, 0.5] s$\\
    $\phi_c$ & coalescence phase & $[0, 2\pi]$\\
    $\cos{\iota}$ & cosine of inclination angle & $[-1, 1]$\\
    $\psi$ & polarization angle & $[0, \pi]$\\
    $\alpha$ & right ascension & $[0, 2\pi]$\\
    $\sin{\delta}$ & sine of declination & $[-1, 1]$\\

    \hline
    \hline
    \end{tabular}
    \caption{Parameters used in the injection-recovery test.}
    \label{tab:parameters}
    \end{center}
\end{table*}

% Show injection pp plot
The result of this injection-recovery campaign is shown in fig. \ref{fig: ppplot}. We
computed the quantile of which the true value lies for each marginalized
distribution, then plotted the cumulative distribution of these quantiles. The
shadow band denotes the 95\% credible interval drawn from a uniform distribution
with the same number of events. We can see most the injection-recovery result
lies within the band drawn from a uniform distribution, showing our inference
results agree well with a uniform distribution. There is a small deviation from
a uniform distribution for the secondary spin $\chi_2$, which is not too
alarming since we are computing the quantile for 11 parameters. Having one of
them lying briefly outside the 95\% band does not mean the inference is bias.

To quantify how well our result agrees with a uniform distribution, we can
compute the Kolmogorov-Smirnov test p-values for each marginalized distribution.
If the p-value is too low, often chosen to be $0.05$, then it means our result
does not agree with a uniform distribution, hence it could be biased. The
p-values for each marginalized distribution are shown in the legend of fig.
\ref{fig: ppplot}. We can see most of them are well above the $0.05$ threshold,
except for $\chi_2$, which is mildly below the threshold. Once again, assuming
these p-values are drawn from a uniform distribution, given $11$ draws (the
number of parameters in our inference), it is not abnormal to have one of the
parameters lies slightly outside the threshold. To assess whether this is
expected, we can compute the combined p-value for these 11 parameters, which is $0.47$.
This shows our inference pipeline performs properly on simulated data.
Indeed, the accuracy of our inference pipeline is consistent with other works\kw{cite}.

@@

\kw{Talk about future development}

>>>>

\section{Result}
\label{sec: Result}
\subsection{Injection-recovery test}

@@

\begin{table}[hbt!]
    \begin{center}
    \begin{tabular}{ l l l }
    \hline
    \hline
    Parameters &  Description & Prior range\\

    $M_c$ & Chirp mass & $[10, 50] M_\odot$\\
    $q$ & Mass ratio & $[0.5, 1]$\\
    $\chi_1$ & Primary dimensionless spin& $[-0.5, 0.5]$\\
    $\chi_2$ & Secondary dimensionless spin & $[-0.5, 0.5]$\\
    $d_L$ & Luminosity distance & $[300, 2000] \textrm{Mpc}$\\
    $t_c$ & Coalescence time & $[-0.5, 0.5] \textrm{s}$\\
    $\phi_c$ & Coalescence phase & $[0, 2\pi]$\\
    $\cos{\iota}$ & Cosine of inclination angle & $[-1, 1]$\\
    $\psi$ & Polarization angle & $[0, \pi]$\\
    $\alpha$ & Right ascension & $[0, 2\pi]$\\
    $\sin{\delta}$ & Sine of declination & $[-1, 1]$\\

    \hline
    \hline
    \end{tabular}
    \caption{Parameters used in the injection-recovery test.}
    \label{tab:parameters}
    \end{center}
\end{table}

% Show injection pp plot
The result of this injection-recovery campaign is shown in fig. \ref{fig:ppplot}. We
computed the quantile of which the true value lies for each marginalized
distribution, then plotted the cumulative distribution of these quantiles. The
shadow band denotes the 95\% credible interval drawn from a uniform distribution
with the same number of events. We can see most the injection-recovery result
lies within the band drawn from a uniform distribution, showing our inference
results agree well with a uniform distribution. There is a small deviation from
a uniform distribution for the secondary spin $\chi_2$, which is not too
alarming since we are computing the quantile for 11 parameters. Having one of
them lying briefly outside the 95\% band does not mean the inference is bias.

To quantify how well our result agrees with a uniform distribution, we can
compute the Kolmogorov-Smirnov test p-values for each marginalized distribution.
If the p-value is too low, often chosen to be $0.05$, then it means our result
does not agree with a uniform distribution, hence it could be biased. The
p-values for each marginalized distribution are shown in the legend of fig.
\ref{fig:ppplot}. We can see most of them are well above the $0.05$ threshold,
except for $\chi_2$, which is mildly below the threshold. Once again, assuming
these p-values are drawn from a uniform distribution, given $11$ draws (the
number of parameters in our inference), it is not abnormal to have one of the
parameters lies slightly outside the threshold. To assess whether this is
expected, we can compute the combined p-value for these 11 parameters, which is $0.47$.
This shows our inference pipeline performs properly on simulated data.
Indeed, the accuracy of our inference pipeline is consistent with other works\kw{cite}.

@@
